\chapter{Introduction}
\section{Electronic voting}
Since 2015, it is possible for Swiss citizens registered in the cantons Geneva and Neuchâtel and living abroad, to vote electronically. However, these systems did not yet meet the requirements in terms of security and transparency, to be accepted as a secure E-Voting platform on a nationwide scale.

One of the requirements that is hardest to achieve, is that a good e-voting system must be transparent and allow an external person to verify, that every protocol participant has abided by the protocol and that only valid votes have been counted. 

Another common problem is the \textbf{insecure platform problem}: If a voters computer is affected by malware, the vote casting process is no longer under the voters control and the candidate selection could be possibly manipulated without the voters notice. It must be \textbf{individually verifiable} to every voter that his intended vote has been received, while at the same time, the voters privacy must be ensured at all times. What sounds like a paradoxon, can be solved by modern cryptography.

A contract was formed between the state of Geneva and the Bern University of Applied Sciences to work out a new protocol which does meet the complex requirements set up by the government. In 2017, the resulting specification document has been officially published and a proof-of-concept / prototype has been successfully implemented by the State of Geneva. 

\section{The CHVote protocol}
The protocol our project is based on, does not originate from us! The concept and specification has been created by Rolf Haenni, Philipp Locher and Reto E. Koenig of the Institute for Security in the Information Society (RISIS) of the Bern University of Applied Sciences. For this project, we have implemented the protocol according to their specification. In this section we summarize the most important aspects of the protocol and establish the terminology for better understanding this document and our application.

\subsection{Actors}
A \textbf{voter} is a person who is eligible to vote in his respective state. Every voter must possess a voting card that has been sent to him prior to an election event and that contains several codes such as the voting code and the confirmation code, which are used to identify the voter during the vote casting process. Every voter is assigned a \textbf{counting circle} which typically corresponds to the voters municipal. This information is required for statistical purposes. 

A voter uses a \textbf{voting client} to participate in an election event, e.g. forming a ballot according to the protocol, by entering his selection, a voting code to cast, and later in the process, his confirmation code to confirm his vote. Verification codes and a finalization code are displayed by the voting client to ensure the voter that his vote has been cast as intended and hasn't been manipulated by a third party.

The \textbf{Election Administrator}, typically a person of the government, sets up the election event by providing the required information such as the candidates or the voters and initiates the generation of the cryptographic electorate data. He is also responsible for tallying the election and publishing the final results.

The \textbf{election authorities} can be seen as some kind of independent election observers. In a CHVote election event there are always multiple election authorities in order to avoid having a single authority that needs to be trusted. The authorities are involved in almost every step of the protocol, starting from generating their shares of the electorate data, shares of a jointly generated public key used for encryption, checking and responding to new ballots and vote confirmations, as well as in the mixing (a measure to ensure anonymity) and decryption phases.

The \textbf{Bulletin Board} acts as a central board over which most communication is done and where all the public data is stored.

The \textbf{Printing Authority} is responsible for printing the voting cards for all voters. Since the printing authority needs to be in possession of all the secret voting credentials, it is a very sensitive point in the protocol. The printed voting cards are handled over to a trusted mailing service for delivery.

\subsection{Pre-Election \& Voting cards}
Before the actual election phase, the vote administrator sets up the election event by entering all required parameters, namely the voters, the elections with their corresponding candidates and the number of candidates a voter can select in this respective election. All election authorities jointly generate the cryptographic data for the whole electorate from which the voting card information is derived. The printing authority combines the information from all election authorities, prints the voting cards and delivers them to the voters by a trusted mailing service. 

A voting card contains several codes, namely:

\begin{itemize}
	\item a voting code
	\item a confirmation code
	\item a finalization code
	\item one verification code for every candidate
\end{itemize}

The \textbf{voting and confirmation codes} are authentication codes and are used to authenticate the voter twice during the vote casting process; the first time with the voting code when he casts his vote, and a second time for confirming his vote. A second authentication code is required because otherwise an attacker who infected a voters computer with malware could just confirm a vote on behalf of the voter after he manipulated the candidate selection and skip the whole verification process w. 

\subsection{Individual verification with oblivious transfer}
As mentioned earlier, one of the big challenges of an evoting-protocol is how it deals with the insecure platform problem: A voting platform that is infected with malware poses the risk that an attacker can manipulate the candidate selection on the vote-casting page after the voter has entered his voting code. 

The CHVote specification suggests a "`Cast-as-intended verification"'-step to allow voters to detect this kind of manipulation: When a voter enters his voting code and the indices of his favored candidates, the voting client forms a \textbf{ballot} containing the voters selection encrypted with the authorities public key, his public voting credential derived from the voting code, and a \textbf{non-interactive zero knowledge proof} which proofs that the voter has formed the ballot according to the protocol and that he has been in knowledge of his voting code, without revealing any information about the voting code.

Every election authority has to check the voters public voting credential, the validity of the ballot proof and that the voter hasn't already cast a vote. The encrypted selection also serves as a query for an oblivious transfer. A \textbf{k-out-of-n oblivious transfer} allows a client to query a server for $k$ messages, without the server knowing what messages the client requested, and without the client learning anything about the other $n-k$ messages. Adapted to the CHVote protocol: The voting client queries the authorities for the corresponding verification codes of the selected candidates, without the authorities learning which candidates the voter has selected, and without revealing any information about the other candidates. 

The voter then checks if the returned verification codes match the codes of the candidates he has chosen on the printed voting card. If the selection was somehow manipulated by malware, the returned verification codes would not match the printed ones and the voter would have to abort the vote casting process. This way the integrity of the vote casting process can be guaranteed even in the presence of malware. In such a case, privacy on the other hand cannot be protected since the malware will learn the plaintext of the voters selection.

Another feature the protocol supports, is that an election event can consist of $t$ multiple parallel elections. In such cases, the voter has to submit a single ballot, which contains his candidate selection for all parallel elections. This raises the question, how the system can verify that a voter has chosen exactly the correct number of candidate in each election, and not for example one less in the first, and one additional candidate in the second election.

The specification suggests the following trick: Assuming an election consists of two parallel elections ($t=2$) with 3 candidates each ($n_1 = 3, n_2 = 3$), of which a voter can select one candidate in each election ($k_1 = k_2 =1$). The verification codes are derived from $n = \sum_{j=1}^{t} n_j$ random points on $t$ polynomials (one for every election event $j$) of degree $k_j - 1$, that each election authority has chosen randomly prior to the election. By learning exactly $k = \sum_{n=1}^{t} k_j$ points on these polynomials, the voting client is able to reproduce these polynomials and therefore is able to calculate a particular point with $x=0$ on these polynomials. The corresponding $y$ values are incorporated into the second credential from which the confirmation code is derived. As a result, only if a voter has been able to reconstruct these polynomials with the returned points by submitting a valid candidate selection, he will be able to confirm the vote that he casted.

\subsection{From homomorphic encryption to mix-networks}

Since there is still a connection between the encrypted ballot and the voter at this point, the encrypted selections are extracted from the ballots as the first step of the post-election phase. In order to anonymize the list of encryptions, every authority performs a cryptographic shuffle with a random permutation and re-encrypts all ciphertexts in order to make it impossible to find out which voter has submitted which encrypted ballot. This is done by using the multiplicative homomorphic property of the ElGamal encryption scheme. A multiplicative homomorphic encryption scheme allows to perform multiplications on the ciphertext such that:

\begin{equation*}Enc(a) \cdot Enc(b) = Enc(a \cdot b)\end{equation*}

The specification suggests multiplying the encryption with the encryption of the neutral element $1$ since this yields a new ciphertext for the exact same plaintext.

\subsection{Distributed trust}
The public key that is used for encrypting the ballots has been jointly generated by all election authorities. Therefore in order to decrypt the result, all authorities must provide their share of the private key. The measure of multiple authorities participating in the whole e-voting process ensures security of the whole election process as long as at least one election authority can be trusted.

\section{Project task}

Understanding such a complex protocol isn't easy and might be the reason why many people still do not trust electronic voting systems. In close consultation with the authors of the CHVote specification, we decided to develop an application that allows users to get a hands-on experience with the CHVote e-voting system and makes it possible to show and explain to an audience how the future of voting in Switzerland might possibly look like.

For this reason we have developed a web-based application which allows to visualize every step of a CHVote election event, from generating the electorate data, to casting and confirming ballots from a voters point of view, to the post-election processes like mixing, decryption and tallying. Opposed to a realistic prototype, the focus on our project is not to implement an e-voting-system that is totally realistic, but more on the visualization.  

As preparatory work, we have implemented all approximately 65 algorithms which were defined as pseudo-code in the CHVote specification document during the course "`Project 2"', which we have finished just before our bachelor thesis. From the resulting set of algorithms we have created a library which we used for implementing the protocol which our application will be built on.